### 2019-06-12 5-Nomenclature/Nomenclature.tex
Typo

% Institution
\nomenclature[A]{ANR}{\textit{Agence Nationale de la Recherche} (French National Research Agency)}
\nomenclature[A]{ENS}{\textit{École Normale Supérieure}}
\nomenclature[A]{CNRS}{\textit{Centre National de la Recherche Scientifique}}
\nomenclature[A]{SCEE}{\textit{Signal, Communication et Électronique Embarquée} (research team in CentraleSupélec, campus of Rennes)}

@@

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_i^{(k)}$}{Mean of arm $k$, arm $k$ at time $t$ (in Chapter~\ref{chapter:6}), arm $k$ for user $j$ (in Chapter~\ref{chapter:5}), arm $i$ in the $k$-th stationary interval (in Chapter~\ref{chapter:6})}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda},$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps ($\Delta^{\text{opt}}$ and $\Delta^{\text{change}}$)}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known before hand by an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau^{(k)}$}{Location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, the parameter for the $\varepsilon$-greedy algorithm, or the drift correction parameter for \CUSUM{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Usually denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}, or a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta(n,\delta)$}{Usually denotes a threshold for the statistical (GLR) tests in Chapter~\ref{chapter:6}}

@@

\nomenclature[L]{$\cH_0$, $\cH_1$, $\cH_2$}{Hypothesis, in Chapters~\ref{chapter:4} and \ref{chapter:6}}
\nomenclature[L]{$d^{(k)}$, $d^{(\ell)}$}{Lower-bound on number of samples for accurate detection of change-points in Chapter~\ref{chapter:6}}
\nomenclature[L]{$\cT$}{In Chapter~\ref{chapter:6}, denote a function in \eqref{def:6:function_T} and a set of time steps in Section~\ref{sub:6:IdeasOptimizations}}

@@

% --------------------------------
% matches Superscripts         > E
\nomenclature[E]{$y^j$}{Usually denotes a variable depending on a player in Chapter~\ref{chapter:5} (for $j\in[M]$), or to distinguish between different independent runs in numerical simulations in Chapter~\ref{chapter:2} (for $j\in[N]$)}
\nomenclature[E]{$y^{(k)}$, $y^{(\ell)}$}{Usually the superscript index $(k)$ or $(\ell)$ denotes a variable in the $k$-th stationary interval, under the  point-of-views of \emph{global} or \emph{local} changes, in Chapter~\ref{chapter:6}}

>>>>

% Institution
% \nomenclature[A]{ANR}{\textit{Agence Nationale de la Recherche} (French National Research Agency)}
% \nomenclature[A]{ENS}{\textit{École Normale Supérieure}}
% \nomenclature[A]{CNRS}{\textit{Centre National de la Recherche Scientifique}}
\nomenclature[A]{SCEE}{\textit{Signal, Communication et Électronique Embarquée} (research team in CentraleSupélec, campus of Rennes)}

@@

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_k^{(i)}$}{Mean of arm $k$, arm $k$ at time $t$ (in Chapter~\ref{chapter:6}), arm $k$ for user $j$ (in Chapter~\ref{chapter:5}), arm $k$ in the $i$-th stationary interval (in Chapter~\ref{chapter:6})}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda},$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps ($\Delta^{\text{opt}}$ and $\Delta^{\text{change}}$)}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known before hand by an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau_k^{(i)}$}{Location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, the parameter for the $\varepsilon$-greedy algorithm, or the drift correction parameter for \CUSUM{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Usually denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}, or a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta(n,\delta)$}{Usually denotes a threshold for the statistical (GLR) tests in Chapter~\ref{chapter:6}}

@@

\nomenclature[L]{$\cH_0$, $\cH_1$, $\cH_2$}{Hypothesis, in Chapters~\ref{chapter:4} and \ref{chapter:6}}
\nomenclature[L]{$d^{(i)}$, $d^{(\ell)}$}{Lower-bound on number of samples for accurate detection of change-points in Chapter~\ref{chapter:6}}
\nomenclature[L]{$\cT$}{In Chapter~\ref{chapter:6}, denote a function in \eqref{def:6:function_T} and a set of time steps in Section~\ref{sub:6:IdeasOptimizations}}

@@

% --------------------------------
% matches Superscripts         > E
\nomenclature[E]{$y^j$}{Usually denotes a variable depending on a player in Chapter~\ref{chapter:5} (for $j\in[M]$), or to distinguish between different independent runs in numerical simulations in Chapter~\ref{chapter:2} (for $j\in[N]$)}
\nomenclature[E]{$y^{(i)}$, $y^{(\ell)}$}{Usually the superscript index $(i)$ or $(\ell)$ denotes a variable in the $i$-th stationary interval, under the  point-of-views of \emph{global} or \emph{local} changes, in Chapter~\ref{chapter:6}}
